Storm surge modelling in the Strait of Georgia

### 2014-10-16 RoughWork/manuscript.tex
added tide table to manuscript

\section{Appendix}\label{sec:appendix}
\begin{table}[h]
\centering 
\begin{tabular}{l l c c c c c c} 
\hline 
& & \multicolumn{3}{c}{M$_2$} & \multicolumn{3}{c}{K$_1$} \\ 
\hline 
            & Station name     & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) \\
\hline 
1           & Port Renfrew     &     &                      &          &     &                      &          \\
2           & Sheringham Point &     &                      &          &     &                      &          \\
3	    & Pedder Bay       &     &                      &          &     &                      &          \\
4           & Esquimalt        &     &                      &          &     &                      &          \\
5           & Victoria         &     &                      &          &     &                      &          \\
6           & Clover Point     &     &                      &          &     &                      &          \\
7           & Finnerty Cove    &     &                      &          &     &                      &          \\
8           & Fulford Harbour  &     &                      &          &     &                      &          \\
9           & Tumbo Channel    &     &                      &          &     &                      &          \\
10          & Patos Island     &     &                      &          &     &                      &          \\
11          & Whaler Bay       &     &                      &          &     &                      &          \\
12          & Tsawwassen       &     &                      &          &     &                      &          \\
13          & Sandheads        &     &                      &          &     &                      &          \\
14          & Point Grey       &     &                      &          &     &                      &          \\
15          & Point Atkinson   &     &                      &          &     &                      &          \\
16          & Gibsons Landing  &     &                      &          &     &                      &          \\
17          & Winchelsea       &     &                      &          &     &                      &          \\
18          & Halfmoon Bay     &     &                      &          &     &                      &          \\
19          & Irvines Landing  &     &                      &          &     &                      &          \\
20          & Powell River     &     &                      &          &     &                      &          \\
21          & Little River     &     &                      &          &     &                      &          \\
22          & Lund             &     &                      &          &     &                      &          \\
23          & Twin Islets      &     &                      &          &     &                      &          \\
24          & Campbell River   &     &                      &          &     &                      &          \\
25          & Maude Island E   &     &                      &          &     &                      &          \\
26          & Nymphe Cove      &     &                      &          &     &                      &          \\
27          & Seymour Narrows  &     &                      &          &     &                      &          \\
28          & Brown Bay        &     &                      &          &     &                      &          \\
29          & Chatham Point    &     &                      &          &     &                      &          \\
30          & Kelsey Bay       &     &                      &          &     &                      &          \\
31          & Yorke Island     &     &                      &          &     &                      &          \\
\hline   
            &  Mean Error      &     &                      &          &     &                      &          \\
            &  RMS Error       &     &                      &          &     &                      &          \\
\hline  
\end{tabular}
\caption{Comparisons of modelled and observed amplitudes and phases. $R$ is the ratio of modelled to observed amplitude. $\Delta \phi$ is the difference between modelled and observed phase. $D$ is the complex difference. }
\label{tab:comparison} 
\end{table}
%May have to include station numbers and locations on a map? Maybe on the contour map, overlay with stations and green/red dots (hopefully mostly green)
%Should we use the new method of calculating tides?

>>>>

\section{Appendix}\label{sec:appendix}
\begin{table}[h]
\centering 
\begin{tabular}{l l l l c c c c c c} 
\hline 
& & & & \multicolumn{3}{c}{M$_2$} & \multicolumn{3}{c}{K$_1$} \\ 
\hline 
            & Station name     & Longitude & Latitude & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) & $R$ & $ \Delta \phi$ (deg) & $D$ (cm) \\
\hline 
1 & Port Renfrew & -124.43 & 48.55 & 1.16 & -9.4 & 16.63  & 1.03 & -4.94 & 4.17 \\
2 & Sheringham Point & -123.92 & 48.38 & 1.19 & -16.47 & 17.95  & 1 & -4.44 & 4.24 \\
3 & Pedder Bay & -123.55 & 48.33 & 0.96 & -27.39 & 15.91  & 0.99 & -2.41 & 2.66 \\
4 & Esquimalt & -123.43 & 48.43 & 0.91 & -23.09 & 14.40  & 0.99 & -1.04 & 1.21 \\
5 & Victoria & -123.37 & 48.42 & 0.89 & -17.77 & 11.62  & 1.04 & -1.83 & 3.22 \\
6 & Clover Point & -123.35 & 48.41 & 0.83 & -17.95 & 13.39  & 1.03 & -2.23 & 3.14 \\
7 & Finnerty Cove & -123.3 & 48.47 & 0.83 & -8.24 & 9.47  & 1.02 & -2.19 & 3.25 \\
8 & Fulford Harbour & -123.45 & 48.77 & 0.82 & -3.08 & 10.78  & 1 & -0.63 & 0.83 \\
9 & Tumbo Channel & -123.11 & 48.79 & 1.05 & 2.03 & 4.43  & 1.04 & 0.66 & 3.34 \\
10 & Patos Island & -122.97 & 48.78 & 1.03 & 0.26 & 2.32  & 1.04 & -1.5 & 3.92 \\
11 & Whaler Bay & -123.33 & 48.89 & 1 & -0.76 & 1.10  & 1.01 & -0.48 & 1.19 \\
12 & Tsawwassen & -123.13 & 48.99 & 1 & 0.92 & 1.31  & 1.01 & 0.19 & 1.09 \\
13 & Sandheads & -123.3 & 49.1 & 1.02 & -1.05 & 2.58  & 1.04 & -0.59 & 3.15 \\
14 & Point Grey & -123.27 & 49.25 & 0.98 & -3.31 & 5.83  & 0.96 & -0.68 & 3.63 \\
15 & Point Atkinson & -123.25 & 49.33 & 1.01 & -0.48 & 1.07  & 1 & -0.56 & 0.94 \\
16 & Gibsons Landing & -123.5 & 49.4 & 0.98 & 0.75 & 2.34  & 1 & 0.96 & 1.47 \\
17 & Winchelsea & -124.08 & 49.3 & 1.01 & -0.19 & 0.78  & 1.01 & 0.51 & 1.30 \\
18 & Halfmoon Bay & -123.92 & 49.52 & 1.01 & -0.15 & 0.83  & 1.01 & 0.15 & 0.72\\ 
19 & Irvines Landing & -124.05 & 49.63 & 1 & -0.32 & 0.59  & 1.01 & 0.24 & 1.12 \\
20 & Powell River & -124.55 & 49.86 & 1 & -1.72 & 3.05  & 1 & -0.01 & 0.43 \\
21 & Little River & -124.92 & 49.74 & 1.03 & 0.07 & 2.54  & 1.01 & 0.33 & 0.73\\ 
22 & Lund & -124.76 & 49.98 & 1.02 & -2.52 & 4.98  & 1.02 & -0.95 & 2.45 \\
23 & Twin Islets & -124.93 & 50.03 & 1.02 & -2.05 & 4.22  & 1.01 & -0.24 & 0.72\\ 
24 & Campbell River & -125.24 & 50.04 & 0.99 & 0.51 & 1.12  & 1 & 0.94 & 1.39 \\
25 & Maude Island E & -125.33 & 50.13 & 1.13 & -10.02 & 12.62  & 0.97 & -1.44 & 2.89\\ 
26 & Nymphe Cove & -125.36 & 50.13 & 1.02 & -5.43 & 6.04  & 0.97 & -0.29 & 2.02 \\
27 & Seymour Narrows & -125.34 & 50.13 & 0.63 & 31.31 & 53.40  & 1.14 & 10.91 & 17.28 \\
28 & Brown Bay & -125.37 & 50.16 & 0.98 & -5.63 & 9.26  & 0.98 & -0.04 & 1.17 \\
29 & Chatham Point & -125.44 & 50.33 & 1.09 & -5.49 & 12.18  & 0.98 & -3.18 & 3.85 \\
30 & Kelsey Bay & -125.96 & 50.39 & 1 & -1.69 & 3.50  & 0.98 & -0.39 & 1.00 \\
31 & Yorke Island & -125.97 & 50.44 & 0.99 & 1.59 & 3.32  & 1.01 & 1.23 & 1.37\\ 
\hline 
&   Mean Error (cm/deg) & & & 4.23  & 6.5 & 8.05   & 1.56 & 1.49 & 2.58 \\
&   RMS Error (cm/deg)  & & & 7.67  & 10.73 & 12.73 & 2.41 & 2.57 & 3.91 \\
\hline  
\end{tabular}
\caption{Comparisons of modelled and observed amplitudes and phases. $R$ is the ratio of modelled to observed amplitude. $\Delta \phi$ is the difference between modelled and observed phase. $D$ is the complex difference. }
\label{tab:comparison} 
\end{table}
%May have to include station numbers and locations on a map? Maybe on the contour map, overlay with stations and green/red dots (hopefully mostly green)
%Should we use the new method of calculating tides?
